---
title: "BIOS 520 HW 1"
author: "Cathy Zhuang"
date: "2023-01-13"
output:
  html_document: default
  word_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/Cathy/Desktop")
library(kableExtra)
library(dplyr)
library(readxl)

captopril <- read_excel("captopril.xls")
captopril$diffs <- captopril$SBP_WK1 - captopril$SBP_WK0

```

Summarize and graph the data to show the differences between the 2 
treatments.

```{r}
boxplot(diffs ~ GROUP, data = captopril, main = "Differences in Blood Pressure after One Week of Treatment")


captopril %>%                               # Summary by group using dplyr
  group_by(GROUP) %>% 
  summarize(min_diff = min(diffs),
            q1 = quantile(diffs, 0.25),
            median = median(diffs),
            mean = mean(diffs),
            q3 = quantile(diffs, 0.75),
            max = max(diffs),
            std_dev = sd(diffs)) %>% 
  kbl(caption = "Summary Statistics of Differences Between the 2 Treatments") %>%
  kable_classic_2(full_width = F) 
```
Perform a statistical test and write 1-2 sentences on the conclusion and interpretation. INCLUDE in canvas submission: One word document including your graph, analysis and brief conclusion.

The statistical test I will perform is a two-sample t test with an alpha of 0.05. First, I will conduct an F test to compare variances:

```{r}
var.test(diffs ~ GROUP, data = captopril) # F test to compare variances
```
Since we fail to reject the hypothesis that the true ratio of variances is not equal to 1, we will assume equal variances for the t test.

```{r}
t.test(diffs ~ GROUP, data = captopril, var.equal = TRUE)
```
From the two-sample t-test with an alpha of 0.05, since our p-value of 0.08592 is larger than alpha, we conclude that the mean change in systolic blood pressure is not different between the captopril group and the placebo group (p=0.0852, 95% CI: -17.19, 1.28 mmHg). The intervention was not effective in reducing systolic blood pressure.




